### 2021-07-11 src/paper/report.tex
Fixed document, some typos, removed duplicated parameter.

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the three
channels for rapid tests. Tests at schools have the smallest effect, which is largely
explained by schools not operating at full capacity during our period of study and the
relatively small number of students.\footnote{18\% of our population are in the education
sector (pupils, teachers, etc.); 46\% are workers outside the education sector.} Almost
40\% come from tests at the workplace. Despite the fact that rapid tests for private
reasons are phased in only late, they make up for more than half of the total effect. The
reason lies in the fact that a substantial share of these tests is driven by an elevated
probability to carry the virus, i.e., showing symptoms of CoViD-19 or following up on a
positive test of a household member. The latter is essentially a form of contact tracing,
which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020,FetzerGraeber2021}.

@@

Our analysis has shown that during the transition to high levels of vaccination and
possibly thereafter, large-scale rapid testing can substitute for some NPIs. This comes
at a fraction of the cost. A week of the fairly strict lockdown in early 2021 is
estimated to have cost around 20~Euros per capita \citep{Wollmershauser2021}; retail
prices for rapid tests were below one Euro in early June 2021. Despite these large
effects, the results on testing likely understate the benefits. Disadvantaged groups are
less likely to be reached by testing campaigns relying on voluntary participation
\citep[e.g.][]{StillmanTonin2021}; at the same time, these groups have a higher risk to
contract CoViD-19 \citep{RKI2021a}. Mandatory tests at school and at the
workplace will extend more into these groups. The same goes for individuals who exhibit
a low level of compliance with CoViD-19-related regulations. Compared to vaccinations,
rapid testing programmes allow a much quicker roll-out, making it arguably the most
effective tool to contain the pandemic in the short run.

>>>>

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the three
channels for rapid tests. Tests at schools have the smallest effect, which is largely
explained by schools not operating at full capacity during our period of study and the
relatively small number of students.\footnote{18\% of our population are in the education
sector (pupils, teachers, etc.); 46\% are workers outside the education sector.} Almost
40\% come from tests at the workplace. Despite the fact that rapid tests for private
reasons are phased in only late, they make up for more than half of the total effect. The
reason lies in the fact that a substantial share of these tests is driven by an elevated
probability to carry the virus, i.e., showing symptoms of CoViD-19 or following up on a
positive test of a household member. The latter is essentially a form of contact tracing,
which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020,Fetzer2020}.

@@

Our analysis has shown that during the transition to high levels of vaccination and
possibly thereafter, large-scale rapid testing can substitute for some NPIs. This comes
at a fraction of the cost. A week of the fairly strict lockdown in early 2021 is
estimated to have cost around 20~Euros per capita \citep{Wollmershauser2021}; retail
prices for rapid tests were below one Euro in early June 2021. Despite these large
effects, the results on testing likely understate the benefits. Disadvantaged groups are
less likely to be reached by testing campaigns relying on voluntary participation
\citep[e.g.][]{StillmanTonin2021}; at the same time, these groups have a higher risk to
contract CoViD-19 \citep{KochInstitut2021a}. Mandatory tests at school and at the
workplace will extend more into these groups. The same goes for individuals who exhibit
a low level of compliance with CoViD-19-related regulations. Compared to vaccinations,
rapid testing programmes allow a much quicker roll-out, making it arguably the most
effective tool to contain the pandemic in the short run.

### 2021-07-11 src/paper/results/rapid_tests_statistics.tex
Fixed document, some typos, removed duplicated parameter.

Next, we show the tests split by whether they are true positive, false positive, true
negative or false negative (see Figure~\ref{fig:rapid_test_results_numbers}) in numbers
per million individuals to make the metric comparable to incidences.
% true positive
The number of true positives (Figure~\ref{fig:rapid_tests_number_true_positive}) rapidly
increases and peaks at the end of April with over 200 cases per million detected through
rapid tests per day. This means that our model suggests that Germany was able to detect
up to 16,600 cases per day that would have likely gone undetected otherwise. The most
powerful tool for detecting cases are the private rapid tests. This is because a large
share of them are targeted, i.e. triggered by events in the household. However, this
does not mean that rapid tests in the workplace or at school are useless. It is rather
the combination of large scale screening at work and in schools and very efficient
follow up tests whenever those screening tests detected a case. Shapley values
(Figure~\ref{fig:2021_scenarios_decomposition_tests}) take this into acount and
assign about 50\% of the overall reduction of case numbers via rapid tests to private
rapid tests with work and school rapid tests accounting for 40\% and 7\%,
respectively.

@@

A similar picture arises, when looking at the false positive rate,
i.e. the share of positive tests that go to people who are not infected.
Figure~\ref{fig:rapid_tests_false_positive_rate} shws that the false
positive rate is very high. On average 60\% to 93\% of positive tests are
received by individuals that are not infected. The false positive rate increases over
time. This is due to the low prevalence of infections in the population, which falls
over time. Again, private rapid tests are an exception with a much lower false
positive rate because those tests are primarily demanded when there is a high likelihood
of beeing infected. The low false negative rate of 0.2\% looks very low. As discussed
above this is deceiving and just a mechanical consequence of a very low prevalence
of the disease and the many rapid tests done by non-infected people.

@@

    \floatfoot{\noindent \textit{Note:}
    The left panel shows the share of positive tests that are given to people who are not
    infected. This share is large as can be expected with a very low baseline rate of
    positive individuals. As the incidence in the population drops, the false positive
    rate increases. An exception are the private rapid tests because they are --
    especially when the incidence is high -- often triggered by events that make it
    likely that the test taker is infected and therefore their false positive rate is
    much lower. The right panel shows the false negative rate in the population, i.e. the
    share of negative test results that are mistakenly given to infected individuals.
    This is very low because there are many truly negative tests in times of low
    incidences and large scale screening tests.
\end{figure}

>>>>

Next, we show the tests split by whether they are true positive, false positive, true
negative or false negative (see Figure~\ref{fig:rapid_test_results_numbers}) in numbers
per million individuals to make the metric comparable to incidences.
% true positive
The number of true positives (Figure~\ref{fig:rapid_tests_number_true_positive}) rapidly
increases and peaks at the end of April with over 200 cases per million detected through
rapid tests per day. This means that our model suggests that Germany was able to detect
up to 16,600 cases per day that would have likely gone undetected otherwise. The most
powerful tool for detecting cases are the private rapid tests. This is because a large
share of them are targeted, i.e. triggered by events in the household. However, this
does not mean that rapid tests in the workplace or at school are useless. It is rather
the combination of large scale screening at work and in schools and very efficient
follow up tests whenever those screening tests detected a case. Shapley values
(Figure~\ref{fig:2021_scenarios_decomposition_tests}) take this into account and
assign about 50\% of the overall reduction of case numbers via rapid tests to private
rapid tests with work and school rapid tests accounting for 40\% and 7\%,
respectively.

@@

A similar picture arises, when looking at the false positive rate,
i.e. the share of positive tests that go to people who are not infected.
Figure~\ref{fig:rapid_tests_false_positive_rate} shows that the false
positive rate is very high. On average 60\% to 93\% of positive tests are
received by individuals that are not infected. The false positive rate increases over
time. This is due to the low prevalence of infections in the population, which falls
over time. Again, private rapid tests are an exception with a much lower false
positive rate because those tests are primarily demanded when there is a high likelihood
of being infected. The low false negative rate of 0.2\% looks very low. As discussed
above this is deceiving and just a mechanical consequence of a very low prevalence
of the disease and the many rapid tests done by non-infected people.

@@

    \floatfoot{\noindent \textit{Note:}
    The left panel shows the share of positive tests that are given to people who are not
    infected. This share is large as can be expected with a very low baseline rate of
    positive individuals. As the incidence in the population drops, the false positive
    rate increases. An exception are the private rapid tests because they are --
    especially when the incidence is high -- often triggered by events that make it
    likely that the test taker is infected and therefore their false positive rate is
    much lower. The right panel shows the false negative rate in the population, i.e. the
    share of negative test results that are mistakenly given to infected individuals.
    This is very low because there are many truly negative tests in times of low
    incidences and large scale screening tests.}
\end{figure}
